Theories of deliberated choice

### 2024-01-24 simple.tex
No HAI, condition required (reworded)

  Given any infinite set $\allargs$, define $I = I^\text{DJ} = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
  Considering any $\hist \in \finite(\allhists)$ and ${\ileadsto} \in I$, pick another relation that coincides on $\hist$ but with another DJ than ${\ileadsto}$. This is possible because $\hist$ is finite, thus there is an argument that is not involved in any of its elements, which can serve as decisive one.
  Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
\end{example}  
\begin{example}[no HAI]
  \label{ex:noHAI}
  Define $I = \set{i_1, i_2, i_3}$ and $\allleadsto$ as follows: $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$. 
  Then $\pi(i_1) = \phi$ and $\pi(i_2) = \pi(i_3) = \emptyset$.
  This satisfies \ref{it:condNotHAI}: considering any $\hist \in \allhists$, if $(1, a) \in \hist$, then $i_2$ collides with $i_1$ on $\hist$, and otherwise, $i_3$ does.
\end{example}  
\begin{remark}[no HAI thanks to condition]
  Whether the condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required remains an open question. Showing that it is required requires an example where,
  defining $Q(\hist, i_1)$ as $\exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$,
  the condition
  $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: Q(\hist, i_1)$ is satisfied, even though
  $[\forall \hist \in \allhists, i_1 \in I: Q(\hist, i_1)]$ is not, thus satisfying $\exists \hist, i_0 \suchthat \pi(i_0) = \emptyset \land ¬Q(\hist, i_0)$.

  Define $I = \set{i_1, …, i_5}$, $\ileadsto[i_1], \ileadsto[i_2], \ileadsto[i_3]$ as in \cref{ex:noHAI} and $\ileadsto[i_4]$ and $\ileadsto[i_5]$ as: $.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_4] ¬\phi$, $a.* \ileadsto[i_4] \phi$, $b.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_5] ¬\phi$, $a.* \ileadsto[i_5] ¬\phi$, $b.* \ileadsto[i_5] \phi$. 
  This satisfies \ref{it:condNotHAI} for the reason given in \cref{ex:noHAI}, and fails $Q(\emptyset, i_4)$.
  This is not possible by starting from \cref{ex:noHAIwithDJ}: given any infinite set $\allargs$, defining some adequate $J = \set{i_0, …}$ and $I = I^\text{DJ} \cup J$ and $\forall i \in I: {\ileadsto} = i$, we get that $i_0$ conflicts on every paths with some individuals in $I^\text{DJ}$.
\end{remark}
\begin{remark}
  Given $J \wsub I$, say that a set of paths discriminates $J$ iff some function associating each path to an answer is compatible with some $j \in J$ (meaning that $f \wsub {\ileadsto[j]}$) and is compatible with no $i \notin J$.
  The condition says that there must be some $p$ and some increasing set of paths $H$ such that $H$ discriminates $J = \pi^{-1}(p)$.
\end{remark}
\begin{remark}
  For failing the condition, I need an infinity of $j$’s (and at least one $i$) who agree on any branch of the history tree? (Meaning relations $\ileadsto[j]$, we don’t care about individuals.)
  No: on any finite branch in the tree, I need that remains one $j$ and one $i$ such that infinite prolongation of the branch will never discriminate them.

>>>>

  Given any infinite set $\allargs$, define $I = I^\text{DJ} = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
  Considering any $\hist \in \finite(\allhists)$ and ${\ileadsto} \in I$, pick another relation that coincides on $\hist$ but with another DJ than ${\ileadsto}$. This is possible because $\hist$ is finite, thus there is an argument that is not involved in any of its elements, which can serve as decisive one.
  Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
\end{example}  
\begin{example}[no HAI]
  \label{ex:noHAI}
  Define $I = \set{i_1, i_2, i_3}$ and $\allleadsto$ as follows: $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$. 
  Then $\pi(i_1) = \phi$ and $\pi(i_2) = \pi(i_3) = \emptyset$.
  This satisfies \ref{it:condNotHAI}: considering any $\hist \in \allhists$, if $(1, a) \in \hist$, then $i_2$ collides with $i_1$ on $\hist$, and otherwise, $i_3$ does.
\end{example}  
\begin{remark}[no HAI condition required]
  The condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required:
  the following example satisfies \ref{it:condNotHAI} but fails the extended version of that condition without that condition.
  In other words, defining $Q(\hist, i_1)$ as $\exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$,
  the example satisfies
  $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: Q(\hist, i_1)$,
  but does not satisfy
  $[\forall \hist \in \allhists, i_1 \in I: Q(\hist, i_1)]$, thus, satisfies 
  $\exists \hist, i_0 \suchthat \pi(i_0) = \emptyset \land ¬Q(\hist, i_0)$.

  Define $I = \set{i_1, …, i_4}$, $\ileadsto[i_1], \ileadsto[i_2], \ileadsto[i_3]$ as in \cref{ex:noHAI} and $\ileadsto[i_4]$ as: $.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_4] ¬\phi$, $a.* \ileadsto[i_4] \phi$, $b.* \ileadsto[i_4] ¬\phi$. 
  This satisfies \ref{it:condNotHAI} for the reason given in \cref{ex:noHAI}, and fails $Q(\emptyset, i_4)$.
\end{remark}
\begin{remark}
  Given $J \wsub I$, say that a set of paths discriminates $J$ iff some function associating each path to an answer is compatible with some $j \in J$ (meaning that $f \wsub {\ileadsto[j]}$) and is compatible with no $i \notin J$.
  The condition says that there must be some $p$ and some increasing set of paths $H$ such that $H$ discriminates $J = \pi^{-1}(p)$.
\end{remark}
\begin{remark}
  For failing the condition, I need an infinity of $j$’s (and at least one $i$) who agree on any branch of the history tree? (Meaning relations $\ileadsto[j]$, we don’t care about individuals.)
  No: on any finite branch in the tree, I need that remains one $j$ and one $i$ such that infinite prolongation of the branch will never discriminate them.
